A simplified dynamic bioenergetic model for coral-*Symbiodinium* symbioses and coral bleaching as an alternate stable state

### 2017-01-11 JTB_supp/JTB_supp.Rmd
fix plotting error

plot(NA, xlim=range(input$L), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
title("DIN=1e-7 mol/L; X=1e-6 mol/L")
apply(res2, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
  with(x[x$sh>0.3, ], {
    points(L, rep(0.3, length(L)), pch="^", col="red")
    points(L, rep(0.29, length(L)), pch=1, col="red", cex=1)
  })
})

plot(NA, xlim=range(input$L), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
title("DIN=1e-6 mol/L; X=2e-6 mol/L")
apply(res3, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
  with(x[x$sh>0.3, ], {
    points(L, rep(0.3, length(L)), pch="^", col="red")
    points(L, rep(0.29, length(L)), pch=1, col="red", cex=1)
  })
})

plot(NA, xlim=range(input$L), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
title("DIN=1e-6 mol/L; X=4e-6 mol/L")
apply(res4, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
  with(x[x$sh>0.3, ], {
    points(L, rep(0.3, length(L)), pch="^", col="red")
    points(L, rep(0.29, length(L)), pch=1, col="red", cex=1)
  })
})

>>>>

plot(NA, xlim=range(input$L), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
title("DIN=1e-7 mol/L; X=1e-6 mol/L")
apply(res2, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
  with(x, if (sh > 0.3) {
    points(L, 0.3, pch="^", col="red")
    points(L, 0.29, pch=1, col="red", cex=1)
  })
})

plot(NA, xlim=range(input$L), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
title("DIN=1e-6 mol/L; X=2e-6 mol/L")
apply(res3, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
  with(x, if (sh > 0.3) {
    points(L, 0.3, pch="^", col="red")
    points(L, 0.29, pch=1, col="red", cex=1)
  })
})

plot(NA, xlim=range(input$L), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
title("DIN=1e-6 mol/L; X=4e-6 mol/L")
apply(res4, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
  with(x, if (sh > 0.3) {
    points(L, 0.3, pch="^", col="red")
    points(L, 0.29, pch=1, col="red", cex=1)
  })
})
